### 2019-02-15 Sections/quality_of_service.tex
indexing
CV QEC, details + ref

\subsection{Continuous-variables}\index{Continuous-variable!Quantum error correction}

@@

It has been proven that QEC of Gaussian noise on Gaussian states, using only Gaussian operations is impossible \cite{bib:PhysRevLett.102.120501}. It is closely related to entanglement distillation, discusses above. Several approaches have since been developed. One proposes to encode information in non-Gaussian CV states, then error correction can be implemented using Gaussian operations, resulting in a Gaussian state \cite{bib:pirandola2004constructing}. Another approach is to error correct on Gaussian states using non-Gaussian operations, similar to the entanglement distillation protocol. It is unclear which one is the most advantageous.

\comment{To do -- can we be a bit more specific about the physical resource requirements and the specific noise models? Specify what Gaussian noise means.}

>>>>

\subsection{Continuous-variables}\index{Continuous-variables!Quantum error correction}

@@

It has been proven that QEC of Gaussian noise on Gaussian states, using only Gaussian operations is impossible \cite{bib:PhysRevLett.102.120501}. It is closely related to entanglement distillation, discusses above. Several approaches have since been developed.

This no-go theorem does not apply if the initial states are non-Gaussian. One can also encode qubits using non-Gaussian continuous-variable states \cite{PhysRevA.64.012310}. Then error correction can be implemented using Gaussian operations, resulting in a Gaussian state. This protocol is known to be fault tolerant, however, the threshold requirements are quite stringent, such as needing the photon number in the squeezed state to be around 20 \cite{PhysRevA.73.012325}.

Another approach is to error correct on Gaussian states using non-Gaussian operations\cite{PhysRevA.67.062320}, similar to the entanglement distillation protocol. It is unclear which one is the most advantageous.

% \comment{To do -- can we be a bit more specific about the physical resource requirements and the specific noise models? Specify what Gaussian noise means.}
